---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# constants: Reference on Constants, Units and Uncertainty

[![Build Status](http://travis-ci.org/Enchufa2/constants.svg?branch=master)](https://travis-ci.org/Enchufa2/constants)
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/constants)](https://cran.r-project.org/package=constants)
[![Downloads](http://cranlogs.r-pkg.org/badges/constants)](https://cran.r-project.org/package=constants)

The **constants** package provides the CODATA internationally recommended values of the fundamental physical constants, provided as symbols for direct use within the R language. Optionally, the values with errors and/or the values with units are also provided if the 'errors' and/or the 'units' packages are installed. The Committee on Data for Science and Technology (CODATA) is an interdisciplinary committee of the International Council for Science which periodically provides the internationally accepted set of values of the fundamental physical constants. This package contains the "2014 CODATA" version, published on 25 June 2015: Mohr, P. J., Newell, D. B. and Taylor, B. N. (2016) <DOI:10.1103/RevModPhys.88.035009>, <DOI:10.1063/1.4954402>.

## Installation

Install the release version from CRAN:

```{r, eval=FALSE}
install.packages("constants")
```

The installation from GitHub requires the [devtools](https://github.com/hadley/devtools) package.

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("Enchufa2/constants")
```

## Example

```{r}
library(constants)

# use the constants in a local environment
with(syms, c0)

# explore which constants are available
lookup("planck constant", ignore.case=TRUE)

# attach the symbols to the search path and use them explicitly
attach(syms)
hbar

# use constants with errors
detach(syms); attach(syms_with_errors)
hbar

# use constants with units
detach(syms_with_errors); attach(syms_with_units)
hbar

# the whole dataset
head(codata)

# number of constants per type
dplyr::count(codata, type, sort=TRUE)
```
